%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage{csquotes}
\usepackage{hyperref}
\usepackage{fontawesome}

% \setlength{\sectionwidth}{1.2in}
\setlength{\resumewidth}{6.5in}
\setlength{\textwidth}{5.2in} % Text width of the document
\setlength{\topmargin}{-0.4in}
\setlength{\textheight}{10.5in}
\setlength{\sectionskip}{2.4ex plus 1ex minus -.2ex}


\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf CHAN \,KHA \,VU} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{
\faPhone \, +38 063 642 8871 \quad
\faEnvelopeO \, \href{mailto:mr.havu@yahoo.com}{mr.havu@yahoo.com} \quad \faStackOverflow \, \href{https://stackoverflow.com/users/4789373/}{FalconUA} \quad  \faGithub \, \href{https://github.com/hav4ik}{hav4ik}}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
% \section{OBJECTIVE}  

% A position in the field of computers with special interests in business applications programming, information processing, and management systems. 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\textit{Master of Science,} in Applied Mathematics \hfill Sep 2017 -- Jun 2019}\\
Taras Shevchenko National University of Kyiv, Faculty of Computer Science and Cybernetics, concentration on Computational Mathematics.
\\
\vspace*{-1.6\baselineskip}\leavevmode

{\textit{Bachelor of Science,} in Applied Mathematics \hfill Sep 2013 -- Jun 2017}\\
Taras Shevchenko National University of Kyiv, Faculty of Computer Science and Cybernetics, concentration on Computational Mathematics.
\\
\vspace*{-1.6\baselineskip}\leavevmode

{\textit{Fall School} on Applied Mathematics and Statistics \hfill Fall 2015}\\
in Kyiv, Ukraine; organized by University of Konstanz, Germany.
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{SKILLS}

C, C++, Python, Scipy, Scikit-Learn, Tensorflow, Caffe, Keras, OpenCV, Android Programming, C\#, SQL, Arch Linux, Unix Shell Scripting, Django, Windows API.
 
\section{RELEVANT\\EXPERIENCE}

{{\sl Samsung Electronics, R\&D Ukraine} \hfill Feb 2017 -- current}\\
Software Engineer at Visual Recognition Laboratory. Primary responsibilities includes:

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Development of the Monocular 3D Scene Reconstruction and Semantic Understanding from single image using State-of-the-Art CNN-based approaches for offline analysis of video streams with general content. Refining results using Homography Estimation, Tracking, and other Computer Vision algorithms.
\item Development, enhancement and optimization of Computer Vision algorithms for Samsung's Virtual and Augmented Reality systems.
\end{itemize}
\vspace*{-1.6\baselineskip}\leavevmode

{{\sl Meetly (Start-Up)} \hfill Dec 2015 -- Apr 2016}\\
A web service which allows its users to post an {\sl Activity Invitation} (e.g. \enquote{\sl Finding someone nearby to build a Quadcopter with me!}), or search for {\sl Activities} around.
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Developed a beta-version backend and designed a RESTful API. Used technologies: Django, PostGIS, Tornado, Redis, PostgreSQL.
\end{itemize}
\vspace*{-1.6\baselineskip}\leavevmode

{{\sl Evolve an RNN-based AI player for racing game} \hfill 2015} \\
Personal project. Using Neuro-Evolution of Augmenting Topologies (NEAT).
 
\section{RESEARCH\\EXPERIENCE}

{{\sl Non-invasive Breast Cancer diagnostics using Computer Vision} \hfill 2017}\\
at Department of Computational Mathematics, Taras Shevchenko National University of Kyiv, collaborating with Institute of Experimental Pathology, Oncology and Radiology of Kyiv.
{Publications:}

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Chan K. Vu, D. A. Klyushin, N. V. Boroday (2017). \enquote{\sl Diagnosing Breast Cancer and Fibroadenomatis by analyzing Interphase Nuclei of Buccal Epithelial: A Hybrid Deep Learning and Feature Engineering Approach}. Paper in process.
\item D. A. Klyushin, D. G. Shervarly, Chan K. Vu, E. V. Golubeva, N. V. Boroday (2017). \enquote{\sl Fractal Analysis of Malignancy-Associated Changes in Interphase Nuclei of Buccal Epithelial}. in Journal of Numerical and Applied Mathematics.
\end{itemize}

 
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%---------------------------------------------------------------------------------------- 

\section{AWARDS AND\\HONORS}

All-Ukrainian Computer Science Competition (3rd place) \hfill 2013 \\
All-Ukrainian {\it Intel ISEF} Competition (3rd place) \hfill 2013 \\
All-Ukrainian Computer Science Competition (3rd place) \hfill 2012 \\
All-Ukrainian {\it Intel ISEF} Competition (3rd place) \hfill 2012 \\
And also won many other programming, physics and mathematics national olympiads and competitions during the years in high school and university.

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE
%---------------------------------------------------------------------------------------- 
 
\section{TEACHING \\ EXPERIENCE}

{{\sl Programming and Advanced Algorithms lecturer} \hfill 2014 -- 2016}\\
at Kyiv-Pechersk Lyceum 171 \enquote{Leader}, Kyiv, Ukraine. Created a flexible training program for the most talented students and prepared them for upcoming olympiads.

%----------------------------------------------------------------------------------------
%	SKILLS AND LANGUAGES
%---------------------------------------------------------------------------------------- 

\section{LANGUAGES}

English (TOEFL iBT 102), Vietnamese (native), Russian (native), Ukrainian (native).

\end{resume}
\end{document}
